The Impact of Alternation

### 2017-05-14 draft.tex
ok

\paragraph{\em Example}
Consider the automaton given in Figure \ref{fig:ex}. First, Algorithm
\ref{alg:predabs} fires the sequence $a$, and since there are no other
formulae than $\bot$ in $\preds$, the successor of $\iota \equiv q_0$
is $\top$ (a). The pivot of $a$ is the root of the ART and the
spuriousness check results in the predicates $\set{q_0,q_1}$, which
are added to $\preds$ and the $\top$ node is deleted. The next time
$a$ is fired, it creates a node labeled $q_1$ and the next sequence
$aa$ creates another node $q_1$ which is covered by the first,
depicted with a dashed arrow (b). The third sequence is $ab$, which
results in a new node $\top$ and triggers a spuriousness check. The
new predicate is $x\leq0\wedge q_2 \wedge y\geq0$ and the pivot is
again the root. Then the entire ART is rebuild with the new predicates
and the sequence $aab$ results in an uncovered node $\top$ (c). The
new pivot is the endpoint of $a$ and the new predicates are $q_1\wedge
q_2$ and $y>x-1 \wedge q_2$. Finally, the ART is rebuilt from the
pivot node and the result is a tree in which all nodes are covered,
thus proving the emptiness of the automaton. \qed

@@

>>>>

\paragraph{\em Example}
Consider the automaton given in Figure \ref{fig:ex}. First, Algorithm
\ref{alg:predabs} fires the sequence $a$, and since there are no other
formulae than $\bot$ in $\preds$, the successor of $\iota \equiv q_0$
is $\top$, in Figure \ref{fig:pa} (a). The pivot of $a$ is the root of
the ART and the spuriousness check yields the predicates $q_0$ and
$q_1$, which are added to $\preds$ and the $\top$ node is removed. The
next time $a$ is fired, it creates a node labeled $q_1$ and the
sequence $aa$ creates another node $q_1$, which is covered by the
first, depicted with a dashed arrow, in Figure \ref{fig:pa} (b). The
third sequence is $ab$, which results in a new uncovered node $\top$
and triggers a spuriousness check. The new predicate obtained from
this check is $x\leq0\wedge q_2 \wedge y\geq0$ and the pivot is again
the root. Then the entire ART is rebuild with the new predicates and
the sequence $aab$ results in an uncovered node $\top$, in Figure
\ref{fig:pa} (c). The new pivot is the endpoint of $a$ and the new
predicates are $q_1\wedge q_2$ and $y>x-1 \wedge q_2$. Finally, the
ART is rebuilt from the pivot node and the result is a tree in which
all nodes are covered, thus proving the emptiness of the automaton, in
Figure \ref{fig:pa} (d). \qed

@@

\begin{figure}[htb]
\begin{tabular}{cc}
\includegraphics[scale=0.42]{figures/IM1.pdf} & \includegraphics[scale=0.42]{figures/IM2.pdf} \\
\footnotesize{(a)} & \footnotesize{(b)} \\
\\
\includegraphics[scale=0.42]{figures/IM3.pdf} & \includegraphics[scale=0.42]{figures/IM4.pdf} \\
\footnotesize{(c)} & \footnotesize{(d)}
\end{tabular}
\caption{Proving Emptiness of the Automaton from Fig. \ref{fig:ex} using Algorithm \ref{alg:impact}}
\label{fig:im}
\end{figure}

\paragraph{\em Example}
We show the execution of Algorithm \ref{alg:impact} on the automaton
from Figure \ref{fig:ex}.  Initially, the procedure fires the sequence
$a$, whose endpoint it labeled with $\top$, in Figure \ref{fig:im}
(a). Since this node is uncovered, it checks the spuriousness of the
counterexample $a$ and refines the label of the node to $q_1$. Since
the node is still uncovered, two successors, labeled with $\top$ are
computed, corresponding to the sequences $aa$ and $ab$, in Figure
\ref{fig:im} (b). The spuriousness check for $aa$ yields the
interpolant $\tuple{q_0,x\leq0\wedge q_2 \wedge y\geq0}$ which
strenghtens the label of the endpoint of $a$ from $q_1$ to $q_1\wedge
x\leq0\wedge q_2\wedge y\geq0$. The sequence $ab$ is also found to be
spurious, which changes the label of its endpoint from $\top$ to
$\bot$, and also covers it. Since the endpoint of $aa$ is not covered,
it is expanded in Figure \ref{fig:im} (c). Both sequences $aaa$ and
$aab$ are found to be spurious, and the enpoint of $aab$, whose label
has changed from $\top$ to $\bot$, is now covered. In the process, the
label of $aa$ has also changed from $q_1$ to $q_1 \wedge y>x-1 \wedge
q_2$, due to the strenghtening with the interpolant from $aab$.
Finally, the only uncovered node is expanded to $aaaa$ and $aaab$,
both found to be spurious, in Figure \ref{fig:im} (d). The refinement
of $aaab$ causes the label of $aaa$ to change from $q_1$ to $q_1
\wedge y>x-1 \wedge q_2$ and this node is now covered by $aa$. Since
its successors are also covered, there are no uncovered nodes and the
procedure returns $\true$. \qed
